---
title: "Ant analyse"
author: "Przemyslaw Rodrigo Klejno"
date: '2022-06-12'
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ant analyse (**Ant**)

Versions of Ant that I have used:

- 1.10.0 - https://archive.apache.org/dist/ant/binaries/apache-ant-1.10.0-bin.zip

- 1.10.5 - https://archive.apache.org/dist/ant/binaries/apache-ant-1.10.5-bin.zip

- 1.9.9 - https://archive.apache.org/dist/ant/binaries/apache-ant-1.9.9-bin.zip

Commands used to analyse project:

- SourceMeterJava -projectName=ant-1.9.9 -projectBaseDir=apache-ant-1.9.9 -resultsDir=Results -runFB=true -FBFileList=filelist-ant-1.9.9.txt

- SourceMeterJava -projectName=ant-1.10.0 -projectBaseDir=apache-ant-1.10.0 -resultsDir=Results -runFB=true -FBFileList=filelist-ant-1.10.0.txt

- SourceMeterJava -projectName=ant-1.10.5 -projectBaseDir=apache-ant-1.10.5 -resultsDir=Results -runFB=true -FBFileList=filelist-ant-1.10.5.txt


## I uploaded results to this github repo:
https://github.com/PRIS2/SourceMeterRodrigo

## Loading data

```{r routes_csv}
Class1.9.9 <- "ant-1.9.9/java/2022-06-12-18-12-47/ant-1.9.9-Class.csv"
Class1.10.5 <- "ant-1.10.5/java/2022-06-12-18-29-12/ant-1.10.5-Class.csv"
Class1.10.0 <- "ant-1.10.0/java/2022-06-12-18-28-05/ant-1.10.0-Class.csv"
```


```{r dataset_csv}
library(readr)
datasetClass1.9.9 <- read_csv(Class1.9.9)
datasetClass1.10.0 <- read_csv(Class1.10.0)
datasetClass1.10.5 <- read_csv(Class1.10.5)
```

## Coupling Between Object classes - CBO

```{r variable_CBO}
cboClass1.9.9 <- datasetClass1.9.9$CBO
cboClass1.10.0 <- datasetClass1.10.0$CBO
cboClass1.10.5 <- datasetClass1.10.5$CBO

Class1.9.9Plot <- table(cboClass1.9.9)
barplot(Class1.9.9Plot,
        main = 'Coupling Between Object classes ANT 1.9.9',
        xlab = 'Coupling Between Object classes',
        ylab = 'Classes')

### in 2 datasets below error occurs, I don't know why, checked a lot of things
Class1.10.0Plot <- table(cboClass1.10.0)
barplot(Class1.10.0Plot,
        main = 'Coupling Between Object classes ANT 1.10.0',
        xlab = 'Coupling Between Object classes',
        ylab = 'Classes')

Class1.10.5Plot <- table(cboClass1.10.5)
barplot(Class1.10.5Plot,
        main = 'Coupling Between Object classes ANT 1.10.5',
        xlab = 'Coupling Between Object classes',
        ylab = 'Classes')

```

## Weighted Methods per Class - WMC

```{r variable_WMC}
wmcClass1.9.9 <- datasetClass1.9.9$WMC
wmcClass1.10.0 <- datasetClass1.10.0$WMC
wmcClass1.10.5 <- datasetClass1.10.5$WMC


tableWMC1.9.9 <- table(wmcClass1.9.9)
barplot(tableWMC1.9.9,
        main = 'Weighted Methods per Class ANT 1.9.9',
        xlab = 'Weighted Methods per Class',
        ylab = 'Classes')

### in 2 datasets below error occurs, I don't know why, checked a lot of things
tableWMC1.10.5 <- table(wmcClass1.10.5)
barplot(tableWMC1.10.5,
        main = 'Weighted Methods per Class ANT 1.10.5',
        xlab = 'Weighted Methods per Class',
        ylab = 'Classes')

tableWMC1.10.0 <- table(wmcClass1.10.0)
barplot(tableWMC1.10.0,
        main = 'Weighted Methods per Class ANT 1.10.0',
        xlab = 'Weighted Methods per Class',
        ylab = 'Classes')
```

## Lack of Cohesion of Methods - LCOM

```{r variable_LCOM}
lcomClass1.9.9 <- datasetClass1.9.9$LCOM5
lcomClass1.10.0 <- datasetClass1.10.0$LCOM5
lcomClass1.10.5 <- datasetClass1.10.5$LCOM5

tableLCOM1.9.9 <- table(lcomClass1.9.9)
barplot(tableLCOM1.9.9,
        main = 'Lack of Cohesion of Methods ANT 1.9.9',
        xlab = 'Lack of Cohesion of Methods',
        ylab = 'Classes')

### in 2 datasets below error occurs, I don't know why, checked a lot of things
tableLCOM1.10.5 <- table(lcomClass1.10.5)
barplot(tableLCOM1.10.5,
        main = 'Lack of Cohesion of Methods ANT 1.10.5',
        xlab = 'Lack of Cohesion of Methods',
        ylab = 'Classes')

tableLCOM1.10.0 <- table(lcomClass1.10.0)
barplot(tableLCOM1.10.0,
        main = 'Lack of Cohesion of Methods ANT 1.10.0',
        xlab = 'Lack of Cohesion of Methods',
        ylab = 'Classes')

```
